---
title: "svgtools: Manipulate SVG template files of diagrams."
author: "Konrad Oberwimmer <konrad.oberwimmer@iqs.gv.at>"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{svgtools: Manipulate SVG template files of diagrams.}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      clean = FALSE,
      run_pandoc = FALSE
    )
  })
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

```

# Purpose


# Reading, displaying and writing SVG files

# Adjusting bar charts
## SVG requirements
Elements (frame, groups) have to be named without spaces or any irregular characters (like _-,;!?).
## Functions

# Adjusting line and/or symbol charts
## SVG requirements
## Functions

# Adjusting scatter plots
## SVG requirements
## Functions

# Changing text in text elements
No special requirements are needed to change text in text elements. The text element can either be named (id-tag in XML) or contain a text to identify it.

Use `changeText()` to manipulate

One thing to be aware of is the 

```{r setup}
library(svgtools)
```
